Software Citation Principles

### 2016-07-21 sc-principles/software-citation-principles.tex
adding description for B.6 and in Google Doc

Requirements for researcher:
\begin{itemize}
\item Name of software
\item Location/repository for the exact release that was used
\item DOI or other persistent handle for that specific release
\item Release has all components necessary for reproducing the work (note that this ideally also means sample inputs and outputs)
\end{itemize}

>>>>

When a researcher wants to understand or verify a research results from another researcher, they
would like to use the same software.  Note that accessing the exact same software is necessary but not sufficient for reproducibility.

Requirements for researcher:
\begin{itemize}
\item Name of software
\item Location/repository for the exact release that was used
\item DOI or other persistent handle for that specific release
\item Release has all components necessary for reproducing the work (Note: this ideally also means sample inputs and outputs)
\end{itemize}
